Alex's Notes and Text Fragments for the JSS Manuscript

### 2022-05-17 paper/paper.Rmd
require blockCV and sperrorest namespaces in respective code chunks

```{r disc-eval, fig.cap='Visualization of one training set / test set combination generated with the leave-one-disc-out method from package sperrorest (method "spcv\\_disc" in mlr3spatiotempcv). The disc has a radius of 300 m and is surrounded by a 400-m buffer.', out.width="40%", echo=FALSE,fig.pos="ht"}
library("mlr3")
library("mlr3spatiotempcv")
task = tsk("ecuador")
rsmp_disc = rsmp("spcv_disc", folds = 100, radius = 300L, buffer = 400L)
rsmp_disc

@@

```{r tile-non-eval, eval=FALSE}
rsmp_tiles = rsmp("spcv_tiles", nsplit = c(3L, 4L))

>>>>

```{r disc-eval, fig.cap='Visualization of one training set / test set combination generated with the leave-one-disc-out method from package sperrorest (method "spcv\\_disc" in mlr3spatiotempcv). The disc has a radius of 300 m and is surrounded by a 400-m buffer.', out.width="40%", echo=FALSE,fig.pos="ht"}
library("mlr3")
library("mlr3spatiotempcv")
requireNamespace("blockCV")
task = tsk("ecuador")
rsmp_disc = rsmp("spcv_disc", folds = 100, radius = 300L, buffer = 400L)
rsmp_disc

@@

```{r tile-non-eval, eval=FALSE}
requireNamespace("sperrorest")
rsmp_tiles = rsmp("spcv_tiles", nsplit = c(3L, 4L))
